% =========================================================================== %
% Preamble                                                                    %
% =========================================================================== %

\documentclass[dvipsnames, 12pt]{article}
\usepackage[utf8]{inputenc}

% Set paper geometry
\usepackage[letterpaper, margin=1.87cm]{geometry}

% Must include this before setting title and author
\usepackage{findlay}

\title{\huge Towards Adaptive Process Confinement
Mechanisms\\{\large COMP5900I Literature Review}}

\author{William Findlay}
% For acmart.cls:
%\affiliation{Carleton University}
%\email{williamfindlay@cmail.carleton.ca}

% Add bibliography:
\addbibresource{references.bib}

% To set sans serif font:
%\renewcommand{\familydefault}{\sfdefault}

\lhead{Towards Adaptive Process Confinement Mechanisms}

% Magic to stop overfull hbox in bibliography!
\emergencystretch=1em

\ExecuteBibliographyOptions{maxbibnames=999}

\setlist[enumerate]{
  leftmargin=*
}

% =========================================================================== %
% Document                                                                    %
% =========================================================================== %

\begin{document}

% Title page
\maketitle
\thispagestyle{plain}
%\pagenumbering{roman}
%\newpage

% Table of Contents, List of Figures, List of Tables, List of Listings
%\begingroup
%\hypersetup{linkcolor=black}
%\tableofcontents
%\newpage
%\listoffigures
%\newpage
%\listoftables
%\newpage
%\lstlistoflistings
%\newpage
%\endgroup

% Reset page numbering
\pagenumbering{arabic}
\setcounter{page}{1}

\vfill
\begin{abstract}
\todo{Come back hither when done.}
\end{abstract}
\vfill
\vfill

\clearpage

% Uncomment for 1.5 spacing:
%\onehalfspacing

\section{Introduction}

Restricting unprivileged access to system resources has been a key focus of
operating systems security research since the inception of the earliest
timesharing computers in the late 1960s and early 1970s \todo{cite}. In its
earliest and simplest form, access control in operating systems meant preventing
one user from interfering with or reading the data of another user. The natural
choice for these early multi-user systems, such as Unix \cite{ritchie1973_unix},
was to build access control solutions centred around the user model---a design
choice which has persisted in modern Unix-like operating systems such as Linux,
OpenBSD, FreeBSD, and MacOS. Unfortunately, while user-centric permissions offer
at least some protection from other users, they fail entirely to protect users
from \textit{themselves} or from their own \textit{processes}.  It was long ago
recognized that finer granularity of protection is required to truly restrict
a process to its desired functionality \cite{lampson1973_a_note}. This is often
referred to as \textit{the process confinement problem} or \textit{the
sandboxing problem}.

\subsection{The Process Confinement Threat Model}

To understand why process confinement is a desirable goal in operating system
security, we must first identify the credible threats to system stability and
security that process confinement addresses. To that end, I first describe three
attack vectors (\crefrange{a:1}{a:3}), followed by three attack goals
(\crefrange{g:1}{g:3}) which highlight just a few of the credible threats posed
by unconfined processes running on a given host.

\begin{enumerate}[label=\bfseries A\arabic*., ref=A\arabic*, labelindent=2em]
    \item \label{a:1} \textsc{Compromised processes.} Unconfined running
    processes have classically presented a valuable target for attacker
    exploitation. With the advent of the Internet, web-facing processes which
    handle untrusted user input are especially vulnerable, particularly as they
    often run with heightened privileges \todo{cite}. The attacker may send
    specially crafted input to the target application, hoping to compromise its
    control flow integrity via a classic buffer overflow, return-oriented
    programming \todo{cite}, or some other means. The venerable Morris Worm,
    regarded as the first computer worm on the Internet, exploited precisely
    such a vulnerability in the \texttt{fingerd} service for Unix \todo{cite}.

    \item \label{a:2} \textsc{Semi-honest software.} Here, I define semi-honest
    software as that which appears to perform its desired functionality, but
    which additionally may perform some set of unwanted actions without the
    user's knowledge. Without putting a proper, external confinement mechanism
    in place to restrict the behaviour of such an application, it may continue
    to perform the undesired actions ad infinitum, so long as it remains
    installed on the host. As a topical example, an \texttt{strace} of the
    popular Discord \todo{cite} voice communication client on Linux reveals that
    it repeatedly scans the process tree and reports a list of \textit{all applications}
    running on the system, even when the \enquote{display active game} feature
    is turned \textbf{off}. This represents a clear violation of the user's
    privacy expectations.

    \item \label{a:3} \textsc{Malicious software.} \todo{Write this}
\end{enumerate}

\begin{enumerate}[label=\bfseries G\arabic*., ref=G\arabic*, labelindent=2em]
    \item \label{g:1} \textsc{Installation of backdoors/rootkits.} \todo{Write this}

    \item \label{g:2} \textsc{Information leakage.} \todo{Write this}

    \item \label{g:3} \textsc{Tampering and denial of service.} \todo{Write this}
\end{enumerate}

\todo{Talk about how the internet has exacerbated this problem}

\subsection{The Case for Adaptive Process Confinement}

Despite decades of work since Lampson's first proposal of the process
confinement problem in 1973 \cite{lampson1973_a_note}, the process confinement
problem remains largely unsolved \cite{crowell2013_confinement_problem}. This
begs the question as to whether our current techniques for process confinement
are simply inadequate for dealing with an evolving technical and adversarial
landscape. In this literature review, I present the status quo in process
confinement, with an emphasis on Unix and modern Unix-like systems such as
Linux.  Further, I present a novel taxonomy, categorizing existing process
confinement mechanisms into \textit{maladaptive}, \textit{semi-adaptive}, and
\textit{adaptive} solutions. Finally, I argue the case for the development and
adoption of \textit{adaptive process confinement mechanisms}.

Here, I define adaptive process confinement mechanisms as those which greatly
help defenders confine their processes and are robust in the presence of
attacker innovation. Roughly, this definition can be broken down into the
following properties:
\begin{enumerate}[label=\bfseries P\arabic*., ref=P\arabic*, labelindent=2em]
    \item \label{p:1} \scshape{Robustness to attacker innovation.} \todo{Write this}
    \item \label{p:2} \scshape{Low adoption effort.} \todo{Write this}
    \item \label{p:3} \scshape{High reconfigurability.} \todo{Write this}
    \item \label{p:4} \scshape{Transparency.} \todo{Write this}
    \item \label{p:5} \scshape{Usability.} \todo{Write this}
\end{enumerate}
Ideally, an adaptive process confinement mechanism should have most---if not
all---of the above properties.

\subsection{Outline}

The rest of this paper proceeds as follows. \todo{List sections and what is in them.}

\section{Traditional Process Confinement Approaches}

\section{Automating Policy Generation}

\section{Automating Policy Audit}

\section{Towards Truly Adaptive Process Confinement}

\subsection{Anomaly Detection Techniques}

\subsection{Extended BPF}

\section{Conclusion}


% Uncomment for bibliography:
\nocite{*} % TODO: Comment this out when done
\clearpage
\printbibliography

\end{document}

% vim:syn=tex
