% =========================================================================== %
% Preamble                                                                    %
% =========================================================================== %

\documentclass[dvipsnames, 12pt]{article}
\usepackage[utf8]{inputenc}

% Set paper geometry
\usepackage[letterpaper, margin=1.87cm]{geometry}

% Must include this before setting title and author
\usepackage{findlay}

\def\bpfcontain{\textsc{BPFContain}}

\title{\Large \bpfcontain: Towards Secure and Usable Containers with eBPF\\{\large COMP5900I Final Project}}
\lhead{\bpfcontain: Towards Secure and Usable Containers with eBPF}

\author{William Findlay}
% For acmart.cls:
%\affiliation{Carleton University}
%\email{williamfindlay@cmail.carleton.ca}

% Add bibliography:
\addbibresource{ref.bib}

% To set sans serif font:
%\renewcommand{\familydefault}{\sfdefault}

% =========================================================================== %
% Document                                                                    %
% =========================================================================== %

\begin{document}

% Note from Anil:
% Final paper needs to make the case for why we shouldn't do this in a kernel
% module --- kernel module would need too much kernelspace code, eBPF is safer,
% etc.

% Title page
\maketitle
\thispagestyle{empty}

\vfill
\begin{abstract}
\noindent
Containers are becoming an increasingly important part of the Linux ecosystem.  Containerized package managers like Snapcraft \cite{snap} and FlatPak \cite{flatpak} enable easy distribution and dependency management for desktop applications, while others such as Docker \cite{docker}, Kubernetes \cite{kubernetes}, and OpenShift \cite{openshift} provide a framework for scaling and composing micro-services, especially in the cloud.  While containers offer a convenient abstraction for distributing and configuring software, they are often used as light-weight alternatives to heavier virtualization techniques, such as virtual machines. Thus, containers can also be thought of as security mechanisms, providing some form of isolation between processes that share the underlying operating system's resources.

Despite this clear security use case, existing container implementations do not consider security a primary goal and often fall back to insecure defaults when the host does not support the correct security abstractions. Further, container security implementations are often complicated, relying on a myriad of virtualization techniques and security abstractions provided by the host operating system to isolate processes and enforce least-privilege. These security abstractions often paradoxically require elevated permissions to use in the first place, resulting in additional security risks when applications can escape confinement.

This paper presents \bpfcontain{}, a novel approach to containers under the Linux kernel designed to rectify these container security issues. \bpfcontain{} is built from the ground up as a light-weight yet secure process confinement solution for modern applications. Implemented in eBPF, an emerging technology for safely extending the Linux kernel, \bpfcontain{} enforces least-privilege in containerized applications without requiring any additional privileges from the host operating system. Users write policy in a high-level language designed to be readable and modifiable without requiring significant security expertise. To further secure the host-container boundary, \bpfcontain{} also enforces a secure implicit policy on all containers and provides additional kernel hardening features to prevent privilege escalation. In this paper, I describe \bpfcontain{}'s design and implementation, evaluate its performance and security, and discuss how it compares with existing container solutions.

\end{abstract}
\vfill
\vfill

\clearpage

% Reset page numbering
\pagenumbering{arabic}
\setcounter{page}{1}

% Table of Contents, List of Figures, List of Tables, List of Listings
%\begingroup
%\hypersetup{linkcolor=black}
%\tableofcontents
%\newpage
%\listoffigures
%\newpage
%\listoftables
%\newpage
%\lstlistoflistings
%\newpage
%\endgroup

% Reset page numbering
\pagenumbering{arabic}
\setcounter{page}{1}

% Uncomment for 1.5 spacing:
\onehalfspacing

\input{sections/01-intro}

\input{sections/02-background}

\input{sections/03-motivation}

\input{sections/04-implementation}

\input{sections/05-evaluation}

\input{sections/06-discussion}

\input{sections/07-related}

\input{sections/08-conclusion}

\input{sections/09-ack}

% Uncomment for bibliography:
\renewcommand\bibfont\footnotesize\singlespacing
\printbibliography

\end{document}

% vim:syn=tex
